---
title: "Covid91 vaccine study Final2020"
author: "Marium Khanum"
date: "10/27/2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.  

The target populations for this study are male, female, drug users and LGBTQ.  

$H_0$:Among the target populations, the vaccine has no effect in terms of preventing Covid-19.  
$H_A$:Among the target populations, the vaccine has an effect in terms of preventing Covid-19.  

# Methods  
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->


Every question is of a Cat~Cat type.  

# Graphical Descriptive Results
# Female Graphical Result
```{r}
dataF = filter(FinalData,sex=="gal")
barchartGC(~infected + treatment,data=dataF)
barchartGC(~infected + treatment,data=dataF, type="percent", main="gal")
           
```
  
Among the females who contracted Covid-19 twice as many took the placebo. Therefore, it appears that the vaccine positively affects the target population and prevents them from getting Covid-19.  

### Numerical Summaries (gal)  
  
```{r}
table1 <- xtabs(~infected + treatment,data=dataF)
rowPerc(table1)
colPerc(table1)
```
  
The numerical summary shows that among all females, only 33.11 were infected with COVID while a higher percentage of females were okay after receiving the vaccine, indicating that it has a positive impact on the female population.  

#Inferential Result (gal)  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

# Male Graphical Result

```{r}
dataG = filter(FinalData,sex=="guy")
barchartGC(~infected + treatment,data=dataG)
barchartGC(~infected + treatment,data=dataG, type="percent", main="guy")
           
```
  
It appears that the vaccine has a negative effect on the guys since they are more likely to get Covid-19 if they receive the vaccine.  
  
### Numerical Summaries (guy)

```{r}
table1 <- xtabs(~infected + treatment,data=dataG)
rowPerc(table1)
colPerc(table1)
```
  
Among all male population, 58.16 percent of males got infected with COVID after receiving the vaccine. This shows that the vaccine makes male population more prone to get the COVID.   
  
#Inferential Result (guy)  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

# LGBTQ Graphical Result

```{r}
DataLGBTQ = filter(FinalData,LGBTQ=="gay")
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent", main="gays")
           
```
  
From the graph above, it appears that the vaccine has a negative effect on gay population since there is more than 60 percent of chance for them to get COVID if they receive the vaccine.  

### Numerical Summaries (gay)  
```{r}
table1 <- xtabs(~infected + treatment,data=DataLGBTQ)
rowPerc(table1)
colPerc(table1)
```
Explain

#Inferential Result (gay)

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

#Drug Users Graphical Result  

```{r}
DataDrugUser = filter(FinalData,DrugUser=="yes")
barchartGC(~infected + treatment,data=DataDrugUser)
barchartGC(~infected + treatment,data=DataDrugUser, type="percent", main="DrugUser")
           
```


### Numerical Summaries (DrugUser)  
```{r}
table1 <- xtabs(~infected + treatment,data=DataDrugUser)
rowPerc(table1)
colPerc(table1)
```
  
Explain  

#Inferential Result (DrugUser)  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
